Deep Learning Project

### 2024-10-11 project/paper-final.tex
Add acknowledgments section
Acknowledged Farooq Mahmud for independently completing the project. This includes all tasks related to model implementation, data processing, training, evaluation, and report writing.

>>>>

\section{Acknowldgements}
This project was completed solely by\textbf{Farooq Mahmud}. All tasks, including the implementation of the TensorFlow code for the GoogLeNet model, data pre-processing, model training and testing, development of the simple sequential model, model evaluation, and writing of the report, were conducted independently.

### 2024-10-11 project/paper-with-edits.tex
Added final latex and PDF's.
Add acknowledgments section
Acknowledged Farooq Mahmud for independently completing the project. This includes all tasks related to model implementation, data processing, training, evaluation, and report writing.

>>>>

\textcolor{red}{
\section{Acknowldgements}
This project was completed solely by\textbf{Farooq Mahmud}. All tasks, including the implementation of the TensorFlow code for the GoogLeNet model, data pre-processing, model training and testing, development of the simple sequential model, model evaluation, and writing of the report, were conducted independently.}
